aaaa

### 2023-11-01 outputs/paper/paper.qmd
Update the citation for R packages

All data was collected and cleaned using the statistical programming language `R` [citation]. The packages used are `tidyverse` [citation], `dplyr` [citation], `stringr` [citation], and `janitor` [citation]. Besides, `here` [citation], `modelsummary` [citation], `girdExtra` [citation], `usmap` [citation], `knitr` [citation], `kableExtra` [citation] are used to analyze the data.

>>>>

All data was collected and cleaned using the statistical programming language `R` [@R]. The packages used are `tidyverse` [@tidyverse], `dplyr` [@dplyr], `stringr` [@stringr], and `janitor` [@janitor]. Besides, `here` [@here], `modelsummary` [@modelsummary], `girdExtra` [@gridExtra], `usmap` [@usmap], `knitr` [@knitr], `kableExtra` [@kableExtra] are used to analyze the data.
